---
title: "Feasibility study on the use of recycling materials for prototyping purposes: a comparative study based on the mechanical resistance"
description: |
  Data Analysis of the Mechanical data
author:
  - name: Fabio Cruz
    url: https://example.com/
    affiliation: UL
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: pdf_document
#output: distill::distill_article
editor_options: 
  chunk_output_type: console
---

```{r setup, include= TRUE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE)
library(tidyverse)
library(here)
library(kableExtra)
library(ggpubr)
## Ggplot Theme setting
theme_set(theme_bw(base_size = 15, base_family = "Palatino")) 
```

First, I look for the paths of all mechanical tests

```{r Path}
# Reading data ----
## Loading the paths
files <-
  here("Datos ensayos") %>% 
  dir( recursive=TRUE, full.names=TRUE, pattern="\\.txt$")
```

## Phase I

Then, I read the `Phase I` tests

```{r Data.Fase.I}
# Reading the Data Fase I ----
# Selecting the Phase I
Fase.1 <- files[1:16]

## Identifying Endommage files----
  # File "PLA virgen/VE-8/VE-8.txt"

# Creating the Nested dataframe ----
Fase.I <- Fase.1 %>%  map( ~ read.delim2(.,  skip=7))
Fase.I <- Fase.I %>%   set_names(Fase.1) %>%   enframe("Type", "Data")

# Organising the dataframe
Fase.I <- 
  Fase.I %>%  
  separate(Type, 
           sep = "/",
           into = c(c(LETTERS[1:9]), c("Phase", "Material", "Sample", "Sample name"))
  ) %>% 
  select(-A, -B, -C, -D, -E, -F, -G, -H, -I)

# Arranging factors ----
Fase.I$Material <- 
  factor(Fase.I$Material,
         levels = c("PLA virgen", "PLA reciclado"),
         labels = c("Virgin" , "Recycled"))
Fase.I <- Fase.I %>% arrange(Material)

## Adding variables to the Original data
Fase.I <-
 Fase.I %>%
 mutate(Data = map(Data, ~ .x %>%
                     mutate (Tensile = (kN / (5 * 13))*(1000),
                                          Strain = mm / 28 )
                   ))

### Function to identify Young Modulus
Young_mod <- function(df) {
  # Filtering the Dataframe
  df <- df %>% filter(Strain >= 0.0005 & Strain <= 0.035 )
  # Doing the linear model
   model= lm(Tensile ~ Strain, data = df)
   E= coefficients(model)[[2]]
  return(E)
}
```


```{r Data.Fase.I}

# Exploratory Graphics for Young Modulus  ----

test <-   Fase.I %>% select(Sample,Material, Data)  %>% unnest(cols = c(Data))
test %>% 
  ggplot(aes(x=Strain, y=Tensile, color= Sample)) +
  geom_point() +
 facet_grid( .  ~  Material ) +
  labs(y="Tensiles strength (MPa)", x="Strain (mm/mm)") 
  
  

# Identifying max Tensile ----
Fase.I <- 
  Fase.I %>% 
  mutate(Young = map_dbl(Data,  Young_mod ),
         Load.max = map_dbl(Data,  function(df) max(df$kN)),
         Tensile.max = map_dbl(Data,  function(df) max(df$Tensile))
         )

## Creating the experimental dataframe with the other factors ----
### Layer height 
Fase.I$LH <- c(0.15, 0.3, 0.15, 0.3, 0.3, 0.15, 0.15, 0.3, 0.15, 0.3, 0.3, 0.15, 0.3, 0.15, 0.15, 0.3) 
Fase.I$LH <- as.factor(Fase.I$LH)

### Infill Pattern 
Fase.I$IP <- c("Tri-hex", "Tri-hex", "Grid", "Grid", 
               "Tri-hex", "Tri-hex", "Grid", "Grid", 
               "Tri-hex", "Tri-hex", "Grid", "Tri-hex", 
               "Tri-hex", "Grid", "Grid", "Grid") 
Fase.I$IP <- as.factor(Fase.I$IP)


### Infill density 
Fase.I$ID <- c(60, 60, 60, 100, 100, 100, 100, 60, 60, 60, 60, 100, 100, 60, 100, 100) 
Fase.I$ID <- as.factor(Fase.I$ID)


### Printing speed 
Fase.I$PS <- c(40, 80, 80, 80, 40, 80, 40, 40, 40, 80, 40, 80, 40, 80, 40, 80 )
Fase.I$PS <- as.factor(Fase.I$PS)

# Final Dataframe
Fase.I <- Fase.I %>% select(Material, LH, IP, ID, PS, Load.max, Young, Tensile.max, Sample, `Sample name`, Data )
```



The database of `Phase I`

```{r Table.PhaseI, }
# Fase.I %>% select(Material:Load.max,Young, Sample) %>% 
#   kbl(booktabs = T, 
#       caption = "Dataframe Phase I") %>%
#   kable_styling(latex_options = "hold_position")

table.fase1 <- 
Fase.I %>% select(Material:Load.max,Young ) %>% 
   set_names("Material", "Layer Height (mm)", "Infill Pattern", "Infill Density (%)", "Printing Speed (mm/s)", "Max Load (kN)", "Young Modulus (MPa)" )

table.fase1$`Max Load (kN)` <- table.fase1$`Max Load (kN)` %>% round( digits=2)
table.fase1$`Young Modulus (MPa)` <- table.fase1$`Young Modulus (MPa)` %>% round( digits=2)

#write_csv2(table.fase1, "../tables/Phase-1.csv")

library(flextable)
table.fase1 %>% flextable() %>%
  set_caption("Results of the Phase I") %>%
  fontsize(size=8, part = "all") %>% 
#  width(j=1:3, width = c(1, 1.5, 1.5)) %>% 
  theme_zebra() 
```

```{r Anova_Young}

Anv_Young <- lm(Young ~ LH + IP + ID + PS + Material , data = Fase.I %>% select(Young, Material:PS))
#summary(Total_model)
anv.fase.1 <- anova(Anv_Young)
summary(anv.fase.1)

total= anv.fase.1$`Sum Sq` %>% sum()

# Percentage of ID
round(anv.fase.1$`Sum Sq`[3]/ total,3)*100
# Percentage of Material
round(anv.fase.1$`Sum Sq`[5]/ total,3)*100


test <- tibble(anv.fase.1) %>% mutate(rownames(anv.fase.1)) %>% set_names("Df", "Sum Sq", "Mean Sq", "F value", "Pr(F)", "Var" ) %>% select(Var, Df:`Pr(F)` ) %>% 
  mutate(`Pr(F)`= round(`Pr(F)`, digits=3),
         `F value` = round(`F value`, digits=3))
  
  #dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3))))

  anv.fase.1 %>% mutate(variable =  rownames(anv.fase.1)) %>%  set_names("Var", "Df", "Sum Sq", "Mean Sq", "F value", "Pr(F)") %>% 
  dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3))))

test[3,5] <- paste0(test[3,5],"*")
test[5,5] <- paste0(test[5,5],"*")


test %>% flextable() %>%
  set_caption("ANOVA results at 95\\% significance level.") %>%
  fontsize(size=10, part = "all") %>% 
#  width(j=1:3, width = c(1, 1.5, 1.5)) %>% 
  theme_zebra() #%>%   

```

### Graphic of the influence of the parameters

I create each boxplot

```{r}
## Comparing the Virgin et Recycling
MT <- 
  Fase.I %>% 
  ggplot(aes(x=Material, y = Load.max )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Max Load (kN)", x="Material type") +
  coord_cartesian(ylim = c(1, 4)) +
  theme(legend.position = "none") 

MT_Y <- 
Fase.I %>% 
  ggplot(aes(x=Material, y = Young )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Young modulus (MPa)", x="Material type") +
  coord_cartesian(ylim = c(500, 1500))+
  theme(legend.position = "none") 


## Comparing the Virgin et Recycling
LH <- 
  Fase.I %>% 
  ggplot(aes(x = LH, y = Load.max )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Max Load (kN)", x="Layer heigth (mm)") +
  coord_cartesian(ylim = c(1, 4)) +
  theme(legend.position = "none") 

LH_Y <- 
  Fase.I %>% 
  ggplot(aes(x = LH, y = Young )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Young modulus (MPa)", x="Layer heigth (mm)") +
  coord_cartesian(ylim = c(500, 1500))+
  theme(legend.position = "none") 

## Infill pattern
IP <- 
  Fase.I %>% 
  ggplot(aes(x = IP, y = Load.max )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Max Load (kN)", x="Infill pattern") +
  coord_cartesian(ylim = c(1, 4))

IP_Y <- 
  Fase.I %>% 
  ggplot(aes(x = IP, y = Young )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Young modulus (MPa)", x="Infill pattern") +
  coord_cartesian(ylim = c(500, 1500))+
  theme(legend.position = "none") 


## Infill density
ID <- 
  Fase.I %>% 
  ggplot(aes(x = ID, y = Load.max )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Max Load (kN)", x="Infill density (%)") +
  coord_cartesian(ylim = c(1, 4))

ID_Y <- 
  Fase.I %>% 
  ggplot(aes(x = ID, y = Young )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( .  ~  ) +
  labs(y="Young modulus (MPa)", x="Infill density (%)") +
  coord_cartesian(ylim = c(500, 1500))


## Infill density
PS <- 
  Fase.I %>% 
  ggplot(aes(x = PS, y = Load.max )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( Load.max  ~ LH + IP ) +
  labs(y="Max Load (kN)", x="Printing speed (mm/s)") +
  coord_cartesian(ylim = c(1, 4))

PS_Y <- 
  Fase.I %>% 
  ggplot(aes(x = PS, y = Young )) +
  geom_boxplot(aes(fill=Material)) +
  #facet_grid( Load.max  ~ LH + IP ) +
  labs(y="Young modulus (MPa)", x="Printing speed (mm/s)") +
  coord_cartesian(ylim = c(500, 1500))
  #theme(legend.position = "none")


```


Plotting the Boxplots

```{r, fig.width=7, fig.height=7}
ggarrange(LH, IP, ID , PS,
          LH_Y, IP_Y, ID_Y , PS_Y,
          ncol = 4, nrow = 2 ,common.legend = TRUE)
#ggsave("../Figures/Phase-1-2-correction.jpg", width=12, height=6, dpi = "print")
```



### Anova Phase I
```{r Anova}
## Creating the Linear Model without interactions
Fase.I_anova <- Fase.I %>% select(Material:PS, Load.max)
Total_model <- lm(Load.max ~ LH+IP+ID+PS+Material , data = Fase.I_anova)
#summary(Total_model)
anv.fase.1 <- anova(Total_model)
```


```{r }
# Plotting Anovoa table
anv.fase.1 %>%  set_names("Df", "Sum Sq", "Mean Sq", "F value", "Pr(F)") %>% 
  kbl(booktabs = T, digits = c(0, 1, 3, 3, 3, 5),
      caption = "ANOVA results at 95\\% significance level",  
      linesep = "")  %>%
  kable_styling(latex_options = c("striped"))
```

### Anova Phase I - Virgin and Recycled
```{r}
## Virgin
Virgen <- Fase.I %>% filter(Material == "Virgin") %>% select(LH:PS, Load.max)
Virgin_model <- lm(Load.max ~ . , data =Virgen )
Virgin_anova <- anova(Virgin_model) 

## Recycled
Recycled <- Fase.I %>% filter(Material == "Recycled") %>% select(LH:PS, Load.max)
Recycled_model <- lm(Load.max ~ . , data =Recycled)
Recycled_anova <- anova(Recycled_model) 

```

Anova for Virgin material
```{r}
Virgin_anova %>%  set_names("Df", "Sum Sq", "Mean Sq", "F value", "Pr(F)") %>% 
  kbl(booktabs = T, digits = c(0, 1, 3, 3, 3, 5),
      caption = "ANOVA Virgin",  
      linesep = "")  %>%
  kable_styling(latex_options = c("striped"))
```

Anova for Recycled material
```{r}
Recycled_anova %>% set_names("Df", "Sum Sq", "Mean Sq", "F value", "Pr(F)") %>% 
  kbl(booktabs = T, digits = c(0, 1, 3, 3, 3, 5),
      caption = "ANOVA Recycled",  
      linesep = "")  %>%
  kable_styling(latex_options = c("striped"))
```


## Phase II
Identifying the Paths
```{r Fase.II}
# Selecting the Phase II----
Fase.2 <- files[17:27]
# Deleting test repetido Recycled 70-RE
Fase.2 <- Fase.2[-4]


# Files missing:``
# PLA reciclado/40-RE.txt

# Reading the Data Fase II ----
## Identifying missing data
Fase.II <- Fase.2 %>%  map( ~ read.delim2(.,  skip=7))
Fase.II <- Fase.II  %>%   set_names(Fase.2) %>%   enframe("Type", "Data")

# Organising datafram ----
Fase.II <- 
  Fase.II %>%  
  separate(Type, 
           sep = "/",
           into = c(c(LETTERS[1:9]), c("Phase", "Material", "Sample", "Sample name"))
  ) %>% 
  select(-A, -B, -C, -D, -E, -F, -G, -H, -I)

# Arranging factors ----
Fase.II$Material <- 
  factor(Fase.II$Material,
         levels = c("PLA virgen", "PLA reciclado"),
         labels = c("Virgin" , "Recycled"))

Fase.II <- Fase.II %>% arrange(Material)

# Calculating max Values ----
Fase.II <- 
  Fase.II %>% 
  mutate(Load.max = map_dbl(Data,  function(df) max(df$kN)),
         )

# Creating final dataframe of Phase II
Fase.II <- 
  Fase.II %>% 
  separate(Sample, 
           sep = "-",
           into = c("ID", "Material2")) %>% 
  select(Material, ID, Load.max)

# As factor the the variables ID
Fase.II$ID <- as.numeric(Fase.II$ID)
```


The database of `Phase II`
```{r Table.PhaseI, include=TRUE, layout="l-body-outset"}
Fase.II %>%
  kbl(booktabs = T,
      caption = "Dataframe Phase II",  
      linesep = "")  %>%
  kable_styling()
```


## Ploting the Graph comparative

```{r Fig.Fase.II}
ggplot(Fase.II, aes(x=ID, y=Load.max, col=Material)) + 
  #aes(col=Material),
  geom_point( size=2 ) + 
  geom_line(data = Fase.II %>% filter(ID < 90), stat="smooth",
            method = "lm", formula = y ~ x, linetype ="dashed", alpha = 0.8, size= 1) +
  geom_line(data = Fase.II %>% filter(ID > 65), stat="smooth",
            method = "lm", formula = y ~ poly(x, 2), linetype ="dotted", alpha = 0.8, size= 1) +
#  stat_smooth(data = Fase.II %>% filter(ID < 90) , method = "lm", formula = y ~ x, se=FALSE, aes(alpha=0.5)) +
#  stat_smooth(data = Fase.II %>% filter(ID > 65) , method = "lm", formula = y ~ x, se=FALSE) +
  #stat_smooth(method = "lm", formula = y ~ poly(x, 2), se=FALSE) +
 #stat_regline_equation(label.y = c(3.9,3.5), label.x = c(40,40) , data = Fase.II, aes(x=ID, y=Load.max, label = paste(..eq.label.., ..adj.rr.label.., sep = '~\n~')),  formula = y ~ poly(x, 2), inherit.aes = TRUE ) +
  annotate("segment", x = 80, xend = 80, y = 1.5, yend = 3,  colour = "blue", linetype = "dashed") +
  coord_cartesian(xlim=c(40, 100), ylim=c(1, 4)) + 
  scale_x_continuous(breaks = c(40, 55, 70, 85, 100)) +
  annotate("text", x = c(50, 90), y = 3.3, label = c("Region A", "Region B"))+
  labs(title="", 
       subtitle="", 
       caption="",
       y="Maximum Load (kN)",
       x="Infill density (%)" ) +
theme(legend.position="top")
#ggsave("../Correciones/Phase-2-corrected.jpg", width=5, height=5, dpi = "print")

# Calculating the reductions
Fase.II %>% group_by(ID) %>% summarise(media = mean(Load.max),                                   
                                       sde = sd(Load.max)) %>% 
  mutate(percentage = (media/3.16)*100)
#100- (1.84 * 100)/3.16
```


## Phase III

Identifying the paths
```{r Fase.III}
# Selecting the Phase III----
Fase.3 <- files[28:57]

# Deleting test repetido Recycled 70-RE
Fase.3 <- Fase.3[1:30]

# Files missing:
#

# Reading the Data Fase II ----
## Identifying missing data
Fase.III <- Fase.3 %>%  map( ~ read.delim2(.,  skip=7))
Fase.III <- Fase.III  %>%   set_names(Fase.3) %>%   enframe("Type", "Data")
#Fase.III

# Organising dataframE ----
Fase.III <- 
  Fase.III %>%  
  separate(Type, 
           sep = "/",
           into = c(c(LETTERS[1:10]), c("Material", "Orientation", "Sample", "Sample name"))
  ) %>% 
  select(-A, -B, -C, -D, -E, -F, -G, -H, -I,-J)

# Arranging factors ----
Fase.III$Material <- 
  factor(Fase.III$Material,
         levels = c( "Virgen", "Reciclado"),
         labels = c( "Virgin", "Recycled" ))

Fase.III$Orientation <- tolower(Fase.III$Orientation)
Fase.III$Orientation <- 
  factor(Fase.III$Orientation,
         levels = c("horizontal", "vertical", "canto"),
         labels = c("Horizontal" , "Vertical", "Edgewise"))


Fase.III <- Fase.III %>% arrange(Material)

# Calculating max Values ----
Fase.III <- 
  Fase.III %>% 
  mutate(Load.max = map_dbl(Data,  function(df) max(df$kN)),
         )

# Creating final dataframe of Phase II
Fase.III <- 
  Fase.III %>% 
  select(Material, Orientation, Load.max)
```

The database of `Phase III`
```{r Table.PhaseII, include=TRUE, layout="l-body-outset"}
Fase.III %>%
  kbl(booktabs = T,
      caption = "Dataframe Phase III",  
      linesep = "")  %>%
  kable_styling()
```


```{r Graph.Fase.III}
# Grafica -----

#Fase.III <- 
Fase.III %>% 
  ggplot(aes(x=Orientation, y=Load.max, colour = Material, group=Material)) + 
  geom_point(size=3) +
  #aes(colour = Material) +
  stat_summary(fun = mean, geom="line") +
  stat_summary(fun = mean, geom="crossbar", width=0.5) +
  labs(title="", 
       subtitle="", 
       caption="",
       y="Maximum Load (kN)",
       x="Build orientation of the printed sample" ) +
  theme(legend.position="top") +
  coord_cartesian(ylim=c(1, 2.25)) +
  scale_y_continuous(limits = c(1, 2.25), breaks = c(1, 1.25, 1.5, 1.75, 2, 2.25))
#ggsave("../Figures/Phase-3.jpg", width=5, height=5, dpi = "print")
```




Reduction of the load values
```{r }
## Calculating the reduction
Reduction <- 
  Fase.III %>% 
  group_by(Material,Orientation) %>% 
  summarise(media = mean(Load.max)) 

Reduction <- Reduction %>% pivot_wider(names_from = Material, values_from = media)
Reduction <- Reduction %>% mutate(reduction = (100 - Recycled*100/Virgin ) )

Reduction %>% 
  kbl(booktabs = T,
      caption = "Reduction of properties according to orientation",  
      linesep = "")  %>%
  kable_styling()
```



## Exporting Tables

```{r}
## Write
#write_csv2(Fase.I, "Phase-1.csv")
#write_csv2(Fase.II, "Phase-2.csv")
#write_csv2(Fase.III, "Phase-3.csv")
```
















































